Sparse Function-space Representation of Neural Networks

### 2023-09-01 workshops/icml-duality/main.tex
improved abstract

\begin{abstract}
Deep neural networks (NNs) are known to lack uncertainty estimates, struggle to incorporate new data, and suffer from catastrophic forgetting. We present a method that mitigates these issues by converting NNs from weight-space to a low-rank function-space representation, via the so-called dual parameters. In contrast to previous work, our sparse representation captures the joint distribution over the entire data set, rather than only over a subset. This offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst retaining predictive performance. We provide proof-of-concept demonstrations with the proposed approach for quantifying uncertainty in supervised learning on UCI benchmark tasks.
\end{abstract}

>>>>

\begin{abstract}
Deep neural networks (NNs) are known to lack uncertainty estimates, struggle to incorporate new data, and suffer from catastrophic forgetting. We present a method that mitigates these issues by converting NNs from weight-space to a low-rank (sparse) function-space representation, via a dual parameterization. Importantly, our sparse representation captures the joint distribution over the entire data set. This offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst retaining predictive performance. We provide proof-of-concept demonstrations with the proposed approach for quantifying uncertainty in supervised learning on UCI benchmark tasks.
\end{abstract}
